Real Time Adaptive Shape Reconstruction for Asteroid Landing

### 2018-10-22 manuscript.tex
Add AAS images adn things

\documentclass[journal]{new-aiaa}
%\documentclass[conf]{new-aiaa} for conference papers
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\setlength\LTleft{0pt}

@@

{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
$A$  & amplitude of oscillation \\
$a$ &    cylinder diameter \\
$C_p$& pressure coefficient \\
$Cx$ & force coefficient in the \textit{x} direction \\
$Cy$ & force coefficient in the \textit{y} direction \\
c   & chord \\
d$t$ & time step \\
$Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
$Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
$f, g$   & generic functions \\
$h$  & height \\
$i$  & time index during navigation \\
$j$  & waypoint index \\
$K$  & trailing-edge (TE) nondimensional angular deflection rate\\
$\Theta$ & boundary-layer momentum thickness\\
$\rho$ & density\\
\multicolumn{2}{@{}l}{Subscripts}\\
cg & center of gravity\\
$G$ & generator body\\
iso	& waypoint index
\end{longtable*}}

@@

\subsection{Headings}
Format the title of your paper in bold, 18-point type, with capital and lower-case letters, and center it at the top of the page. The names of the authors, business or academic affiliation, city, and state/province follow on separate lines below the title. The names of authors with the same affiliation can be listed on the same line above their collective affiliation information. Author names are centered, and affiliations are centered and in italic type. The affiliation line for each author includes that author’s city, state, and zip/postal code (or city, province, zip/postal code and country, as appropriate). The first footnote (bottom of first page) contains the job title and department name, and AIAA member grade for each author. Author email addresses may be included also.

Major headings in the template (``sections'' in the \LaTeX{} template commands) are bold 11-point font and centered. Please omit section numbers before all headings unless you refer frequently to different sections. Use Roman numerals for major headings if they must be numbered.

Subheadings (``subsections'' in the \LaTeX{} template commands) are bold, flush left, and either unnumbered or identified with capital letters if necessary for cross-referencing sections within the paper. There must be at least 2 of all subheadings and sub-subheadings. If there is only a single subheading or sub-subheading, please italicize the title of the subheadings, followed by a period, and run it into the text paragraph.

Sub-subheadings (``subsubsections'' in the \LaTeX{} template commands) are italic, flush left, and either unnumbered or numbered with Arabic numerals (1, 2, 3, etc.) if necessary for cross-referencing sections within the paper.

\subsection{Abstract}
An abstract appears at the beginning of Full-Length Papers, Regular Articles, and Express Articles. (Survey and Design Forum Papers, History of Key Technologies Papers, invited lectures, and Technical/Engineering Notes do not include abstracts.) The abstract is one paragraph (not an introduction) and complete in itself (no reference numbers). It should indicate subjects dealt with in the paper and state the objectives of the investigation. Newly observed facts and conclusions of the experiment or argument discussed in the paper must be stated in summary form; readers should not have to read the paper to understand the abstract. Format the abstract bold, indented 3 picas (1/2 in.) on each side, and separated from the rest of the document by two blank lines.

\subsection{Nomenclature}
Papers with many symbols may benefit from a nomenclature list that defines all symbols with units, inserted between the abstract and the introduction. If one is used, it must contain all the symbology used in the manuscript, and the definitions should not be repeated in the text. In all cases, identify the symbols used if they are not widely recognized in the profession. Define acronyms in the text, not in the nomenclature.

\subsection{Biographies}
Survey Papers and some Full-Length Papers include author biographies. These biographies are one paragraph each and should use the abstract formatting style.

\subsection{Footnotes and References}
Footnotes, where they appear, should be placed above the 1'' margin at the bottom of the page. To insert footnotes into the template, use the Insert>Footnote feature from the main menu as necessary. Footnotes are formatted automatically in the template, but if another medium is used, should appear in superscript as symbols in the sequence, *, $\dag$, $\ddag$, \S, \P, **, $\dag\dag$, $\ddag\ddag$, \S\S, etc.

List and number all references at the end of the paper. Corresponding bracketed numbers are used to cite references in the text \cite{vatistas1986reverse}, including citations that are an integral part of the sentence (e.g., ``It is shown in \cite{dornheim1996planetary} that\ldots '') or follow a mathematical expression: ``$A^{2} + B = C$ (Ref.~\cite{terster1997nasa}).'' For multiple citations, separate reference numbers with commas \cite{peyret2012computational,oates1997aerothermodynamics}, or use a dash to show a range \cite{volpe1994techniques,thompsonspacecraft,chi1993fluid}. Reference citations in the text should be in numerical order.

In the reference list, give all authors' names; do not use ``et al.'' unless there are six authors or more. Papers that have not been published should be cited as ``unpublished''; papers that have been submitted or accepted for publication should be cited as ``submitted for publication.'' Private communications and personal website should appear as footnotes rather than in the reference list.

References should be cited according to the standard publication reference style (for examples, see the ``References'' section of this template). Never edit titles in references to conform to AIAA style of spellings, abbreviations, etc. Names and locations of publishers should be listed; month and year should be included for reports and papers. For papers published in translation journals, please give the English citation first, followed by the original foreign language citation.

\subsection{Figures and Tables}
Insert tables and figures within your document; they may be either scattered throughout the text or grouped all together at the end of the file. Do not insert your figures in text boxes. Figures should have no background, borders, or outlines. In the \LaTeX{} template, use the ``caption'' command to type caption text. Captions are bold with a single tab (no hyphen or other character) between the figure number and figure description. See the Table 1 example for table style and column alignment. If you wish to center tables that do not fill the width of the page, simply highlight and “grab” the entire table to move it into proper position.

\begin{table}[hbt!]
\caption{\label{tab:table1} Transitions selected for thermometry}
\centering
\begin{tabular}{lcccccc}
\hline
& Transition& & \multicolumn{2}{c}{}\\\cline{2-2}
Line& $\nu''$& & $J'' $& Frequency, cm$^{-1}$& $FJ$, cm$^{-1}$& $G\nu $, cm$^{-1}$\\\hline
a& 0& P$_{12}$& 2.5& 44069.416& 73.58& 948.66\\
b& 1& R$_{2}$& 2.5& 42229.348& 73.41& 2824.76\\
c& 2& R$_{21}$& 805& 40562.179& 71.37& 4672.68\\
d& 0& R$_{2}$& 23.5& 42516.527& 1045.85& 948.76\\
\hline
\end{tabular}
\end{table}

Line drawings must be clear and sharp. Make sure that all lines and graph points are dark and distinct and that lettering is legible; 8- to 10-point type is suitable for artwork that is sized to fit the column width (3 ¼ in.). Keep the lettering size and style uniform both within each figure and throughout all of your illustrations. Place figure captions below each figure, and limit caption length to 20-25 words. If your figure has multiple parts, include the labels “a),” “b),” etc., below and to the left of each part, above the figure caption. Please verify that the figures and tables you mention in the text actually exist. When citing a figure in the text, use the abbreviation “Fig.” except at the beginning of a sentence. Do not abbreviate “Table.” Number each different type of illustration (i.e., figures and tables) sequentially with relation to other illustrations of the same type.

Figure labels must be legible after reduction to column width (preferably 8--10 points after reduction).

All tables are numbered consecutively and must be cited in the text; give each table a definitive title. Be sure that you have a minimum of two columns (with headings) and two rows to constitute a proper table; otherwise reformat as a displayed list or incorporate the data into the text. Plan tables to fit the column width (3 ¼ in.) or the journal page width (7 in.). Position a double rule at the top and bottom of each table and single rule under the column headings; do not use shading, border lines, or vertical rules between table columns. Position each table in the text close to where it is cited

\subsection{Equations}
Equations are numbered consecutively, with equation numbers in parentheses flush right, as in Eq.~\eqref{sample:equation}. Insert a blank line on either side of the equation. To insert an equation into the \LaTeX{} document, use the \verb|\begin{equation}...\end{equation}| command environment.

A sample equation is included here, formatted using the preceding instructions:

\begin{equation}
\label{sample:equation}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = [\sigma r_2/(2\mu_0)]\int^{\infty}_0\exp(-\lambda|z_j-z_i|)\lambda^{-1}J_1 (\lambda r_2)J_0 (\lambda r_i\,\lambda {\rm d}\lambda)
\end{equation}

Be sure that symbols in your equation are defined in the Nomenclature or immediately following the equation. Also define abbreviations and acronyms the first time they are used in the main text. (Very common abbreviations such as AIAA and NASA, do not have to be defined.)

\subsection{General Grammar and Preferred Usage}
Use only one space after periods or colons. Hyphenate complex modifiers: ``zero-field-cooled magnetization.'' Insert a zero before decimal points: ``0.25,'' not ``.25.'' Use ``\si{\centi\meter\squared}'' not ``cc.''

A parenthetical statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within parenthesis.) Use American, not English, spellings (e.g., “color,” not “colour”). The serial comma is preferred: “A, B, and C” instead of “A, B and C.”

Be aware of the different meanings of the homophones “affect” (usually a verb) and “effect” (usually a noun), “complement” and “compliment,” “discreet” and “discrete,” “principal” (e.g., “principal investigator”) and “principle” (e.g., “principle of measurement”). Do not confuse “imply” and “infer.”

\section{Conclusion}
Although a conclusion may review the main points of the paper, it must not replicate the abstract. A conclusion might elaborate on the importance of the work or suggest applications and extensions. Do not cite references in the conclusion. Note that the conclusion section is the last section of the paper to be numbered. The appendix (if present), funding information, other acknowledgments, and references are listed without numbers.

@@

\section*{Acknowledgments}
An Acknowledgments section, if used, \textbf{immediately precedes} the References. Individuals other than the authors who contributed to the underlying research may be acknowledged in this section. The use of special facilities and other resources also may be acknowledged.

\bibliography{sample}

>>>>

\documentclass[journal]{new-aiaa}
%\documentclass[conf]{new-aiaa} for conference papers
\usepackage{AAS_packages}
% \usepackage[utf8]{inputenc}

% \usepackage[version=4]{mhchem}
% \usepackage{longtable,tabularx}
% \setlength\LTleft{0pt}

@@

% {\renewcommand\arraystretch{1.0}
% \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
% $A$  & amplitude of oscillation \\
% $a$ &    cylinder diameter \\
% $C_p$& pressure coefficient \\
% $Cx$ & force coefficient in the \textit{x} direction \\
% $Cy$ & force coefficient in the \textit{y} direction \\
% c   & chord \\
% d$t$ & time step \\
% $Fx$ & $X$ component of the resultant pressure force acting on the vehicle \\
% $Fy$ & $Y$ component of the resultant pressure force acting on the vehicle \\
% $f, g$   & generic functions \\
% $h$  & height \\
% $i$  & time index during navigation \\
% $j$  & waypoint index \\
% $K$  & trailing-edge (TE) nondimensional angular deflection rate\\
% $\Theta$ & boundary-layer momentum thickness\\
% $\rho$ & density\\
% \multicolumn{2}{@{}l}{Subscripts}\\
% cg & center of gravity\\
% $G$ & generator body\\
% iso	& waypoint index
% \end{longtable*}}

@@

% \section{Multi-resolution Landing Area Refinement}\label{sec:landing_refinement}

% The shape update approach presented is designed with autonomous operations in mind. 
% It is based on an initial coarse shape estimate that is iteratively updated with range measurements of the surface.
% Furthermore, the original mesh is uniformly distributed and as a result many small topological features such as rocks or small craters are not be captured by the shape model. 
% However, these small features are critical for surface operations and safe landings.
% In addition, it would be computationally prohibitive to have a uniformly high resolution mesh.
% In this section, we extend the previous shape update approach to enable a much higher fidelity in a specific location.

% Mixed resolution surface meshes are routinely used in finite element and geometric modeling applications~\cite{botsch2010}.
% As shown in Reference~\citenum{mcmahon2017}, utilizing mixed resolution shape models for asteroid missions offers the potential of reduced computational demands.
% The computational cost of the polyhedron potential model, given by~\cref{eq:potential}, is roughly proportional to the number of faces in the shape model.
% As a result, a uniformly high resolution shape would quickly become intractable for real time operations.
% However, utilizing a mixed resolution approach allows for a high fidelity in a smaller mission critical area, such as a landing site, with a limited impact on the computational cost.

% The selection of a landing site will typically require a vast quantity of data and weigh a multitude of possible metrics, such as scientific value, hardware constraints, timing and communication limits, or safety considerations. 
% In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
% This approach allows for a spacecraft to autonomously select and land on small body.

% The surface slope is computed according to the method developed in Reference~\cite{scheeres1996}.
% Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
% At the center of each face, \( f_i = \begin{bmatrix} f_x & f_y & f_z \end{bmatrix} \), we compute a modified surface acceleration as
% \begin{align}\label{eq:surface_force}
%     U_m = \omega^2 \begin{bmatrix} f_x \\ f_y \\ 0 \end{bmatrix} + \begin{bmatrix} U_x \\ U_y \\ U_z \end{bmatrix},
% \end{align}
% where \( \omega \in \R^1 \) is the angular velocity of the asteroid and \( U_i \) is computed from~\cref{eq:attraction}.
% Then the surface slope can be computed from
% \begin{align}\label{eq:surface_slope}
%     \cos \parenth{ \pi - \phi } = \frac{\vc{n}_f \cdot U_m}{\norm{U_m}},
% \end{align}
% where \( \phi \in \R^1 \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
% If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.

% Additionally, we compute the distance, using~\cref{eq:geodesic_distance}, between the spacecraft state and each face of the asteroid. 
% Finally, we also assign a random science value to the surface in the form of a two dimensional Gaussian.
% Utilizing these metric, a landing site is chosen to minimize the surface cost given as
% \begin{align}\label{eq:surface_cost}
%     J_l =  J_{\text{distance}} - J_{\text{science}},
% \end{align}
% where the surface slope is considered a hard constraint such that any candidate landing site must satisfy \( \phi \leq \phi_m \).

% \paragraph{Mesh Refinement}\label{sec:refinement}

% Once a suitable landing site is selected, the surrounding area is isolated and refined by adding new vertices and faces in the specified area.
% The goal of refinement, or more generally remeshing, is given a mesh ( or a portion of it), compute another mesh whose elements satisfy some quality metrics while suitably approximating the original mesh.
% In this work, we utilize the isotropic remeshing algorithm implemented in the Computational Geometry and Algorithms Library (CGAL).
% This algorithm uses an iterative method which repeatedly splits long edges, collapses short edges, and relocates vertices until all edges are approximately the desired target edge length.
% % TODO Think about adding PMP 6.12 image here

% For example,~\cref{fig:cube_remesh} shows the isotropic remeshing result for the selected faces of a unit cube.
% The original unit cube is composed of \num{8} vertices and \num{12} faces.
% The two triangular faces of the visible side of the cube are selected for the isotropic remeshing operation as shown in~\cref{fig:cube_original_mesh}.
% A target edge length of \num{0.1} is selected for these faces and used to generate~\cref{fig:cube_refine_mesh}.
% The two large triangular faces are divided into a number of smaller triangular faces.
% Furthermore, the additional faces are all approximately the same size and preserve the original surface of the cube.
% After the isotropic remeshing operation the number of vertices has increased from \num{8} to \num{140}.
% \begin{figure}[htbp]
%     \centering
%     \subcaptionbox{Original Cube\label{fig:cube_original_mesh}}{\includegraphics[width=0.25\textwidth]{figures/original_cube.jpg}}~
%     \subcaptionbox{Remeshed Cube\label{fig:cube_refine_mesh}}{\includegraphics[width=0.25\textwidth]{figures/remesh_cube.jpg}}
%     \caption{Example of isotropic remeshing of a face of a cube\label{fig:cube_remesh}}
% \end{figure}

% In order to demonstrate the multi resolution surface refinement we require a true shape model that contains small scale surface features.
% In this dissertation, we utilize the true radar shape model of asteroid 4769 Castalia.
% However, the shape model is not highly detailed as it does not contain small craters or surface features.
% In order to apply the landing refinement process we augment a small portion of the mesh with some additional features and utilize the mesh update scheme shown previously to update the surface.
% The augmented model of Castalia is shown in~\cref{fig:castalia_refinement}.
% \Cref{fig:castalia_refinement} shows that the increased resolution is required in order to reconstruct these small surface details.

\section{Numerical Examples}\label{sec:reconstruction_examples}

In this section, we demonstrate the use of the incremental shape reconstruction algorithm.
The approach is used to iteratively reconstruct the shape of several asteroid given LIDAR measurements.
We utilize radar shape models of asteroids \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\).
The examples demonstrate the full dynamic simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.

The nonlinear controllers described previously are used to control both the translational and rotational states of the vehicle.
Throughout the simulation the control inputs are computed using the current shape estimate of the asteroid. 
As measurements are collected, the spacecraft autonomously updates its shape estimate and uses this estimate to compute the control inputs and desired future states.
These simulations demonstrate the ability of a spacecraft to autonomously explore and maneuver around an unknown small body.

We consider two simulations about asteroids \num{52760} and Castalia.
The asteroids are assumed to constantly rotate about the \( \vc{f}_3 = \vc{e}_3\) axis according to the parameters given in~\cref{tab:dynamic_asteroids}.
Furthermore, the state of the asteroid, namely the rotation matrix \( R_A \), is assumed to be known based on ground measurements or previous data.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lcc}
        \toprule
        Property & \num{4769} Castalia & (\num{52760}) \num{1998} \(\text{ML}_{14}\) \\
        \midrule
        Semi-major axes(\si{\kilo\meter}) & \( 0.8065 \times 0.4905 \times 0.413 \) & \( 1.1 \times 1.1 \times 1.1 \) \\
        Rotational Period (\si{\hour}) & \num{4.095} & \num{14.98} \\
        Density (\si{\gram\per\centi\meter^3}) & \num{2.1} & \num{2.1} \\
        Vertices & \num{2048}  & \num{8192} \\
        Faces & \num{4092} & \num{16320} \\
        \bottomrule
    \end{tabular}
    \caption{Asteroid properties for dynamic exploration~\label{tab:dynamic_asteroids}}
\end{table}
At the beginning of the simulation the spacecraft is assumed to lie on the inertial \( e_1 \) axis, i.e.\ \( x_0 = \begin{bmatrix} x_0 & 0 & 0 \end{bmatrix} \si{\kilo\meter} \).
In addition, at the initial state the spacecraft is orientated such that the \( b_1 \) axis is aligned with the inertial \( e_2 \) axis.
In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat{e}_3)\).
The shape reconstruction phase of the simulation is performed over \SI{15000}{\second}, over which time the spacecraft will take LIDAR measurements of the surface at \SI{1}{\hertz}.
Once the total uncertainty has been reduced sufficiently the spacecraft maneuvers to a ``home'' position aligned with the \( f_1 \) axis of the asteroid.

\paragraph{Asteroid 52760 Reconstruction}

Asteroid (\num{52760}) \num{1998} \(\text{ML}_{14}\) was discovered in \num{1998} and is near Earth asteroid of the Apollo group and classified as a potentially hazardous body.
The asteroid is roughly spherical with a mean radius of approximately \SI{1}{\kilo\meter}.
The initial shape estimate is assumed to be spherical with approximately the same number of vertices as the truth model.
\Cref{fig:52760_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
Due to the roughly spherical shape of the asteroid large portions of the surface are quickly modified to match the measurements.
In addition~\cref{fig:52760_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}%
    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}

    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}%
    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/52760/truth.jpg}}
    \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760. The images colored according to the shape uncertainty. Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
\end{figure}

\paragraph{Asteroid 4769 Castalia Reconstruction}

Asteroid 4769 Castalia is a small near Earth asteroid of the Apollo group.
In addition, it is classified as a potentially hazardous object with a closed approach distance of less than \SI{0.05}{\astronomicalunit}.
Castalia was discovered in \num{1989} and is the first asteroid to be modeled using radar imagery~\cite{hudson1994}.
Castalia is composed of two distinct lobes suggesting that it is a contact binary of two smaller objects held together by their mutual gravity.
\Cref{fig:castalia_weights_reconstruction} show the shape reconstruction at several discrete points during the simulation.
In addition~\cref{fig:castalia_weights_reconstruction} displays the vertex uncertainty \( w_i \) as a colormap on the surface. 
Areas of high uncertainty are denoted in yellow while areas of low uncertainty are in purple/blue.
Within \SI{50}{\percent} of the simulation span the spacecraft is able to achieve an accurate estimate of the true shape of Castalia.

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:castalia_partial_weights_0}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:castalia_partial_weights_25}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_3749.jpg}}%
    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:castalia_partial_weights_50}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_7499.jpg}}

    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:castalia_partial_weights_75}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_11249.jpg}}%
    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:castalia_partial_weights_100}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/partial_weights_14998.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:castalia_weights_truth}}{\includegraphics[trim={15cm 10cm 15cm 10cm},clip,height=0.5\textheight,width=0.3\textwidth,keepaspectratio]{figures/mesh_update/castalia/truth.jpg}}
    \caption[Asteroid Castalia shape reconstruction with uncertainty]{Incremental reconstruction of asteroid Castalia. The images colored according to the shape uncertainty. Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:castalia_weights_reconstruction}}
\end{figure}

\Cref{fig:castalia_metrics} shows the total normalized uncertainty and percent error for the volume estimate. 
The plots show that the reconstruction converges to an accurate shape estimate after approximately \SI{8000}{\second}.
In addition, the volume estimate is initially a much larger value but quickly converges to the true value.
\begin{figure}[htbp]
    \centering
    \input{tikz/castalia_metrics.tikz}
    \caption{Normalized uncertainty and volume percent error for Castalia\label{fig:castalia_metrics}}
\end{figure}
The spacecraft autonomously navigates around asteroid Castalia to best minimize the cost function in~\cref{eq:control_cost}.

% \paragraph{Castalia Landing Site Selection}

% With an appropriate shape estimate, the spacecraft can autonomously transition from a shape reconstruction to a landing mode.
% Based on the shape estimate we seek to determine the best location to land. 
% In reality, any landing site selection would be based on a wide variety of factors and constraints, however we highlight a few which can be determined autonomously and from the shape estimate.
% The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.
% Areas which violate the slope constraint of \( \phi < \SI{5}{\degree} \) are excluded from further consideration.
% \begin{figure}[htbp]
%     \centering
%     \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}%
%     \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
%     \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
% \end{figure}

% The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
% We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
% Landing sites which are closer will be considered preferentially over those at a larger distance.
% \Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
% The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
% \begin{figure}[htbp]
%     \centering
%     \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}%
%     \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
%     \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
% \end{figure}
% We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
% The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
%     \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
% \end{figure}
% After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.

% \paragraph{Castalia Landing Site Refinement}
% One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
% This detail provides a much higher fidelity data source than ground based measurements. 
% In order to emulate this in the simulation we augment the shape model of Castalia with several small craters and outcroppings as shown in~\cref{fig:castalia_refinement}.
% However, these small features would be difficult to capture with the current low resolution shape model of approximately \num{4000} faces.
% The lower number of faces is useful for the evaluation of the polyhedron potential model, it is not ideal for the capture of minute surface features. 
% As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.
% \Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
% \begin{figure}[htbp]
%     \centering
%     \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
%     \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
%     \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
% \end{figure}

% The increased number of faces and vertices in the landing area allows for the capture of the small surface features.
% \Cref{fig:castalia_refinement} shows that given LIDAR measurements alone and the shape reconstruction algorithm that the small features are effectively estimated.
% \begin{figure}[htbp]
%     \centering
%     \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
%     \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
%     \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
% \end{figure}

\paragraph{Castalia Vertical Descent}

The final phase of the simulation is to utilize the estimated shape model and vertically descend to the desired landing site. 
This is accomplished using the closed loop control of the vehicle and a trajectory which transitions from the home position to the surface over \SI{3600}{\second}.
The landing trajectory, using the estimated shape, is visualized in the asteroid frame in~\cref{fig:castalia_landing}.
During the vertical descent the vehicle is able to accurately track the desired trajectory using the estimated shape to compute the gravitational potential.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/asteroid_trajectory.jpg}
    \caption{Vertical descent onto 4769 Castalia~\label{fig:castalia_landing}}
\end{figure}

\section{Conclusions}

This paper developed a Bayesian update scheme to reconstruct the shape of a small body from range measurements. 
The approach allows for a local update operation that is able to reconstruct the shape in real time. 
This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require signification computational resources.
Next, an optimal guidance scheme is derived which determines the desired state to best update the shape estimate. 
This allows for a spacecraft to autonomously maneuver and reconstruct the shape of a small body without operator intervention.
% Finally, a mixed resolution shape representation is presented to allow for an increased fidelity in a specific region of the asteroid.
% This allows for a much greater shape accuracy in a local area while avoiding the computational costs associated with a uniformly high resolution mesh.
Several numerical examples were presented which demonstrates the approach on a number of real asteroids.

@@

\section{Acknowledgement}
This research is supported in part by NSF under the grant CMMI-1335008.

\bibliography{library}
